---
title: "Report3"
author: "Cao Fei, He Ling, Man Zhaolong, Zhen qi"
date: "2020/11/2"
output:
  pdf_document: default
  html_document:
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
require(reshape2)
require(ggplot2)
require(ggthemes)
theme_set(theme_minimal())
require(GGally)
require(ggExtra)
require(maxLik)
```


```{r Load_Data}
# Use your paths
source("../../Code/R/imagematrix.R")
load("../../Data/Binary/bright.Rdata")
load("../../Data/Binary/UrbanHV.Rdata")
load("../../Data/Binary/dark.Rdata")
# Inspect what they are in the Environment window

typeof(bright)
dim(bright)
range(bright)

channal<-1
vUrbanHV <- data.frame(UHV=as.vector(bright[,,channal]))
summary(vUrbanHV)
```




```{r img_plot}

plot(imagematrix(normalize(bright[,,channal])))
ecdf.bright <- ecdf(unlist(vUrbanHV))
eq.bright <- ecdf.bright(unlist(vUrbanHV))
dim(eq.bright) <- dim(bright[,,channal])
plot(imagematrix(eq.bright))

<<<<<<< HEAD
plot(imagematrix(normalize(log(bright[,,channal]))))


=======
>>>>>>> 7edd2a5ffbcf39845b86de3b9be84b720fa9d853
```

```{r Graphical_EDA_BoxplotAndHistogram}
ggplot(vUrbanHV, aes(x=vUrbanHV$UHV)) +
  geom_histogram(aes(y=..density..),
                 bins=nclass.FD(unlist(vUrbanHV)),
                 col="black", fill="white") +
  ylab("Density") +
  xlab("Intensity") 
<<<<<<< HEAD
=======

ggplot(vector.bright, aes(x=bright)) +
  geom_histogram(aes(y=..density..),
                 bins=nclass.FD(unlist(vector.bright)),
                 col="black", fill="white") +
  ylab("Density") +
  xlab("Intensity range:(0-4e6)") +
  xlim(0,4e6)


ggplot(vector.bright, aes(x=bright)) +
  geom_histogram(aes(y=..density..),alpha=0.5, fill="#6495ED", color="black",bins=nclass.FD(unlist(vector.bright))/100) +
  ylab("Histogram")+
  xlim(0,4e6)
```
>>>>>>> 7edd2a5ffbcf39845b86de3b9be84b720fa9d853

ggplot(vUrbanHV, aes(x=vUrbanHV$UHV)) +
  geom_histogram(aes(y=..density..),
                 bins=nclass.FD(unlist(vUrbanHV)),
                 col="black", fill="white") +
  ylab("Density") +
  xlab("Intensity range:(0-4e6)") +
  xlim(0,4e6)


<<<<<<< HEAD
ggplot(vUrbanHV, aes(x=vUrbanHV$UHV)) +
  geom_histogram(aes(y=..density..),alpha=0.5, fill="#6495ED", color="black",bins=nclass.FD(unlist(vUrbanHV))/25) +
  ylab("Histogram")+
  xlim(0,4e6)
```


## The first distribution -- the (SAR) Gamma distribution

=======
>>>>>>> 7edd2a5ffbcf39845b86de3b9be84b720fa9d853

The distribution expression is $f_{\Gamma}(z;L,\mu)=\frac{L^{L}}{\mu^{L} \Gamma(L)} z^{L-1}exp{\{- \frac{Lz}{\mu}\}}$.

1.Moment Estimation (L=1)

$$
\begin{cases}
E(z)=\mu \\
Var(z)=\frac{\mu ^{2}}{L}=\mu^{2}
\end{cases}
$$

According to the above formula, we can get the estimated value of the parameter.

$$
\begin{cases}
\hat{\mu}=E(z)\\
\hat{L}=\frac{E(z)^2}{Var(z)}=1
\end{cases}
$$


2.Maximun Likelihood Estimation

The likelihood function is expressed as $g(Z;L,\mu)=\prod \limits_{i=0}^n f_{\Gamma}(z_{i};L,\mu)=\prod \limits_{i=1}^{n} \frac{L^{L}}{\mu^{L}\Gamma(L)} z_{i}^{L-1}exp{\{- \frac{Lz_{i}}{\mu}\}}=(\frac{L^{L}}{\mu^{L} \Gamma(L)})^{n} \cdot (\prod \limits_{i=1}^n z_{i})^{L-1}exp{\{- \frac{L}{\mu} \prod \limits_{i=1}^n z_{i}\}}$.
The logarithmic likelihood function is expressed as $ln(g(L,\mu))=n \cdot ln(\frac{L^{L}}{\mu^{L}\cdot\Gamma(L)})+(L-1)\sum\limits_{i=1}^{n} ln(z_{i})-\frac{L}{\mu}\sum\limits_{i=1}^n z_{i}$.

The maximum likelihood estimation of $\mu$ can be obtained by taking the derivative with respect to $\mu$ ($\frac{\partial ln(g(Z;L,\mu))}{\partial \mu}=n\cdot \frac{\mu^{L}\Gamma(L)}{L^{L-1}}\cdot(-\frac{L^{L}}{\Gamma(L)\mu^{L+1}})+\frac{L}{\mu^{2}}\sum\limits_{i=1}^nz_{i}$) and setting the partial derivative equal to 0 ($-\frac{n}{\mu}+\frac{1}{\mu^2}\sum\limits_{i=1}^nz_{i}=0$).

The estimate of parameter $\mu$ is $\frac{1}{n}\sum\limits_{i=1}^nz_{i}$.

## The second distribution -- the $G_{I}^{0}$ distribution



The distribution expression is $f_{Z}(z;\alpha,\gamma,L)=\frac{L^{L}\Gamma(L-\alpha)}{\gamma^{\alpha}\Gamma^(L) \Gamma(-\alpha)} \frac{z^{L-1}}{(\gamma+Lz)^{L-\alpha}}$.
The k-order moment of Z is expressed as $E(Z^{k})=(\frac{\gamma}{L})^k\frac{\Gamma(-\alpha-k)}{\Gamma(-\alpha)}\frac{\Gamma(L+k)}{\Gamma(L)}$.

1.Moment Estimation (L = 1)

$$
\begin{cases}
E(z)=\frac{\gamma}{-\alpha-1} \\
Var(z)=E(z^{2})-(E(z))^{2}=\gamma^2\frac{\Gamma(-\alpha-2)}{\Gamma(-\alpha)}\frac{\Gamma(1+2)}{\Gamma(1)}=\frac{2\gamma^{2}}{(-\alpha-1)(-\alpha-2)}-(\frac{\gamma}{-\alpha-1})^{2}
\end{cases}
$$

By means of the above formulation, we can obtained the moment estimate of the parameter.

$$
\begin{cases}
E(z)=\frac{\gamma}{-\alpha-1} \\
Var(z)=\frac{\gamma^{2}\alpha}{(\alpha+1)^2(\alpha+2)}
\end{cases}
$$
According to the above formula, we can get the estimated value of the parameter.


$$
\begin{cases}
\alpha=-2-\frac{2(E(z))^2}{(E(z))^2+var(z)}\\
\gamma=E(z)\cdot(2+\frac{2(E(z))^2}{(E(z))^2+var(z)})
\end{cases}
$$



2.Maximun Likelihood Estimation

The likelihood function is expressed as $g(Z,1;\alpha,\gamma)=\prod \limits_{i=0}^n f_{Z}(z_{i};\alpha,\gamma,L)=\prod \limits_{i=1}^{n} \frac{L^{L}\Gamma(L-\alpha)}{\gamma^{\alpha}\Gamma(L) \Gamma(-\alpha)} \frac{z_{i}^{L-1}}{(\gamma+Lz_{i})^{L-\alpha}}$.

The logarithmic likelihood function is expressed as $ln(g(Z,1;\alpha,\gamma))=ln\frac{\Gamma(1-\alpha)}{\gamma^{\alpha}\Gamma(-\alpha)}+\sum\limits_{i=1}^nln\frac{z_{i}}{\gamma+z_{i}}+\alpha\sum\limits_{i=1}^nln(\gamma+z_{i})=ln(-\alpha)-\alpha ln(\gamma)+\sum\limits_{i=1}^nlnz_{i}+(\alpha-1)\sum\limits_{i=1}^nln(\gamma+z_{i})$.

The maximum likelihood estimation of $\alpha$ and $\gamma$ can be obtained by taking the derivative with respect to $\alpha$ and $\gamma$ and setting the partial derivative equal to 0.

$$
\begin{cases}
\frac{\partial ln(g(Z,1;\alpha,\gamma))}{\partial \alpha}=\frac{1}{\alpha}-ln\gamma+\sum\limits_{i=1}^nln(\gamma+z_{i})=0\\
\frac{\partial ln(g(Z,1;\alpha,\gamma))}{\partial \gamma}=-\frac{\alpha}{\gamma}-(\alpha-1)\sum\limits_{i=1}^n\frac{1}{\gamma+z_{i}}=0
\end{cases}
$$

By simplifying the above equation, we can get:

$$
\begin{cases}
\alpha=\frac{1}{ln\gamma-\sum\limits_{i=1}^n ln(\gamma+z_{i})}=0\\
-\gamma+\sum\limits_{i=1}^n\frac{1}{\gamma+z_{i}}[1-ln\gamma+\sum\limits_{i=1}^nln(\gamma+z_{i})]=0
\end{cases}
$$

According to the relevant codes provided by the teacher, the maximum likelihood estimation of parameters $alpha$ and $\gamma$ can be obtained.



```{r gammaSAR_Distributions}



dgammaSAR <- function(x, Looks, mean) {
  
  dgamma(x, shape=Looks, rate=Looks/mean)
  
}


```

```{r G0_Distributions}

dGI0 <- function(z, p_alpha, p_gamma, p_Looks) {
  
  
  return( 
    ( p_Looks^p_Looks * prod(seq(p_Looks-p_alpha)) * z^(p_Looks-1) ) / 
    (p_gamma^p_alpha * prod(seq(-p_alpha)) * prod(seq(p_Looks)) * (p_gamma + z*p_Looks)^(p_Looks-p_alpha)) 
  )
  

}

```

```{r G0_estimator}

# comparison

GI0.Estimator.m1m2 <- function(z, L) {
  m1 <- mean(z)
  m2 <- mean(z^2)
  m212 <- m2/m1^2
    
  a <- -2 - (L+1) / (L * m212)
  g <- m1 * (2 + (L+1) / (L * m212))
  
  return(list("alpha"=a, "gamma"=g))
}


LogLikelihoodLknown <- function(params) {
  
  p_alpha <- -abs(params[1])
  p_gamma <- abs(params[2])
  p_L <- abs(params[3])
  
  n <- length(z)
  
  return(
    n*(lgamma(p_L-p_alpha) - p_alpha*log(p_gamma) - lgamma(-p_alpha)) + 
      (p_alpha-p_L)*sum(log(p_gamma + z*p_L)) 
  )
}

```


```{r bright}
# comparison
<<<<<<< HEAD
vUrbanHV <- data.frame(UHV=as.vector(bright[,,channal]))
=======
vUrbanHV <- data.frame(UHV=as.vector(bright))
>>>>>>> 7edd2a5ffbcf39845b86de3b9be84b720fa9d853
m<-mean(vUrbanHV$UHV)
L<-1


estim.Urban <- GI0.Estimator.m1m2(vUrbanHV$UHV, L)
z <- vUrbanHV$UHV
estim.UrbanML <- maxNR(LogLikelihoodLknown, 
                       start=c(estim.Urban$alpha, estim.Urban$gamma,1), 
                       activePar=c(TRUE,TRUE,FALSE))$estimate[1:2]

# comparison


a_estimate_1t <- estim.Urban$alpha
g_estimate_1t <- estim.Urban$gamma

a_estimate_2t <- estim.UrbanML[1]
g_estimate_2t <- estim.UrbanML[2]

<<<<<<< HEAD
intensity <- seq(1e-10, 5e6, length.out = 1e5)
=======
intensity <- seq(1e-10, 4e6, length.out = 1e5)
>>>>>>> 7edd2a5ffbcf39845b86de3b9be84b720fa9d853
dExp <- dgammaSAR(intensity,Looks=L, mean=m)
dGI0Mom <- dGI0(intensity, p_alpha=a_estimate_1t, p_gamma=g_estimate_1t, p_Looks=L)
dGI0ML <- dGI0(intensity, p_alpha=a_estimate_2t, p_gamma=g_estimate_2t, p_Looks=L)



df.densities <- data.frame(intensity, dExp, dGI0Mom, dGI0ML)
densities.flat <- melt(df.densities, 
                       measure.vars = c("dExp", "dGI0Mom", "dGI0ML"))

names(densities.flat) <- c("Intensity", "Density", "value")

ggplot(data=vUrbanHV, aes(x=UHV)) +
geom_histogram(aes(y=..density..), col="black",
<<<<<<< HEAD
bins=nclass.FD(unlist(vUrbanHV))/50) +
=======
bins=nclass.FD(unlist(vUrbanHV))/100) +
>>>>>>> 7edd2a5ffbcf39845b86de3b9be84b720fa9d853
geom_line(data=densities.flat, aes(x=Intensity, y=value, col=Density),
lwd=1.5, alpha=.7) +
xlab("Intensities from the bright") +
ylab("Histogram, and fitted Exponential and G0 Laws") +
ggtitle("Restricted Histogram and fitted densities") +
theme_few()+
<<<<<<< HEAD
xlim(0,5e6)
=======
xlim(0,4e6)
>>>>>>> 7edd2a5ffbcf39845b86de3b9be84b720fa9d853


```

The green line is derived from the moment estimation method and the blue line is derived from the maximun likelihood estimation method.

At the same time, we estimate the parameters of other data sets: UrbanHV and dark, and the results are shown as follows.

#UrbanHV dataset

```{r UrbanHV}

# comparison

vUrbanHV <- data.frame(UHV=as.vector(UrbanHV))
m<-mean(vUrbanHV$UHV)
L<-1


estim.Urban <- GI0.Estimator.m1m2(vUrbanHV$UHV, L)
z <- vUrbanHV$UHV
estim.UrbanML <- maxNR(LogLikelihoodLknown, 
                       start=c(estim.Urban$alpha, estim.Urban$gamma,1), 
                       activePar=c(TRUE,TRUE,FALSE))$estimate[1:2]

# comparison


a_estimate_1t <- estim.Urban$alpha
g_estimate_1t <- estim.Urban$gamma

a_estimate_2t <- estim.UrbanML[1]
g_estimate_2t <- estim.UrbanML[2]

intensity <- seq(1e-10, 3e5, length.out = 1e5)
dExp <- dgammaSAR(intensity,Looks=L, mean=m)
dGI0Mom <- dGI0(intensity, p_alpha=a_estimate_1t, p_gamma=g_estimate_1t, p_Looks=L)
dGI0ML <- dGI0(intensity, p_alpha=a_estimate_2t, p_gamma=g_estimate_2t, p_Looks=L)



df.densities <- data.frame(intensity, dExp, dGI0Mom, dGI0ML)
densities.flat <- melt(df.densities, 
                       measure.vars = c("dExp", "dGI0Mom", "dGI0ML"))

names(densities.flat) <- c("Intensity", "Density", "value")

ggplot(data=vUrbanHV, aes(x=UHV)) +
geom_histogram(aes(y=..density..), col="black",
<<<<<<< HEAD
bins=nclass.FD(unlist(vUrbanHV))/50) +
=======
bins=nclass.FD(unlist(vUrbanHV))/100) +
>>>>>>> 7edd2a5ffbcf39845b86de3b9be84b720fa9d853
geom_line(data=densities.flat, aes(x=Intensity, y=value, col=Density),
lwd=1.5, alpha=.7) +
xlab("Intensities from the UrbanHV") +
ylab("Histogram, and fitted Exponential and G0 Laws") +
ggtitle("Restricted Histogram and fitted densities") +
theme_few()+
xlim(0,3e5)

```


#dark set

```{r dark}

# comparison

<<<<<<< HEAD
vUrbanHV <- data.frame(UHV=as.vector(dark[,,channal]))
=======
vUrbanHV <- data.frame(UHV=as.vector(dark))
>>>>>>> 7edd2a5ffbcf39845b86de3b9be84b720fa9d853
m<-mean(vUrbanHV$UHV)
L<-1


estim.Urban <- GI0.Estimator.m1m2(vUrbanHV$UHV, L)
z <- vUrbanHV$UHV
estim.UrbanML <- maxNR(LogLikelihoodLknown, 
                       start=c(estim.Urban$alpha, estim.Urban$gamma,1), 
                       activePar=c(TRUE,TRUE,FALSE))$estimate[1:2]

# comparison


a_estimate_1t <- estim.Urban$alpha
g_estimate_1t <- estim.Urban$gamma

a_estimate_2t <- estim.UrbanML[1]
g_estimate_2t <- estim.UrbanML[2]

intensity <- seq(1e-10, 3e4, length.out = 1e5)
dExp <- dgammaSAR(intensity,Looks=L, mean=m)
dGI0Mom <- dGI0(intensity, p_alpha=a_estimate_1t, p_gamma=g_estimate_1t, p_Looks=L)
dGI0ML <- dGI0(intensity, p_alpha=a_estimate_2t, p_gamma=g_estimate_2t, p_Looks=L)



df.densities <- data.frame(intensity, dExp, dGI0Mom, dGI0ML)
densities.flat <- melt(df.densities, 
                       measure.vars = c("dExp", "dGI0Mom", "dGI0ML"))

names(densities.flat) <- c("Intensity", "Density", "value")

ggplot(data=vUrbanHV, aes(x=UHV)) +
geom_histogram(aes(y=..density..), col="black",
bins=nclass.FD(unlist(vUrbanHV))/50) +
geom_line(data=densities.flat, aes(x=Intensity, y=value, col=Density),
lwd=1.5, alpha=.7) +
xlab("Intensities from the dark") +
ylab("Histogram, and fitted Exponential and G0 Laws") +
ggtitle("Restricted Histogram and fitted densities") +
theme_few()+
xlim(0,3e4)

```
